A Recipe for Scavenging \textcolor{blue}{in Vertebrates} - the natural history of a behaviour

### 2016-08-11 response_letter.tex

We would like to thank the editor, subject editor and reviewers for their comments. By bringing attention to elements of the manuscript that require more careful communication we believe that you have helped us to significantly improve our manuscript. In this submission we have clarified these areas and added a body of work to bolster the conclusions drawn from our work. Please see below where we consider each of your points in turn.
For improved clarity in this document and in the manuscript, we have highlighted our responses in \textcolor{blue}{blue}.

\section{Recommendation by the Subject Editor (anonymous):}
Three experienced reviews have evaluated your manuscript.
Two of them are extremely critical of several aspects related to to the general handcraft and novelly of the review.
The third reviewer is more positive, while making substantial recommendations for improvement of the manuscript.
Should you be able to address all of the reviewers comments in a much revised version of the manuscript I would happy to reconsider the manuscript for consideration in Ecography and the E4 Award.
This is not a provisional acceptance, since the manuscript would need to be revised again.

\smallskip

\textcolor{blue}{As we note below, we feel our earlier manuscript did not capture the hierarchy we had in mind.
This updated version is more explicit in terms of the structure where we now highlight the sections and subsections.
Regarding the novelty of our manuscript, we have changed our introduction which was regarded as too similar to deValult et al. (2003) and argue our case for what we consider inevitable overlap with Beasley et al. (2015).
We now more carefully explain how our qualitative framework can be used to understand scavenging in extinct species.} 
%KH I feel this is a bit weak. While we aknoledge the envitable overlap with Beasely et al we more carefully popint towards how this builds on out qualitative frameworks of how our understanding of extant scavangign can be exxtended to extinct species.

@@

\section{Reviewer: 1}
This paper attempts to synthesize literature on traits that enable scavenging behavior in extant and extinct vertebrates.
The paper is mostly well written, and most (but not all) pertinent literature sources are included.

\textcolor{blue}{Thank you}

I do worry about the lack of novelty of the manuscript, and what I perceived as haphazard organization.

\textcolor{blue}{We feel we have now more clearly outlined the structure of the paper by including an updated figure one explicitly showing the breakdown of the chapters and their link to foraging ecology. This also more clearly highlights the novel aspect of our review, of building a qualitative framework base on foraging ecology to identify the potential levels of scavenging in extinct species and systems and pointing towards possible methods to better focus on certain systems, such as energetic models.}

@@

Here are some specific issues that should be addressed in my opinion:

\begin{enumerate}
\item{Abstract: Scavenging can be difficult to observe, but probably no more so than predation.
Also, using experimental carcasses, scavenging is actually quite easy to observe.}

\textcolor{blue}{We emphasise that food webs have tended to lump all carnivory into predation and it is with extinct species that we have no observational evidence.
We now note measures often used in dietary analysis, such as stomach contents and stable isotope analysis, are unable to distinguish between scavenging and predation. We emphasis that the subsequent need for extensive behavioral data has led to food webs have tending to lump all carnivory into predation and this is particularly likely with extinct species. (lines 53-56)}

@@

\item{Abstract: You should point out that your ``scale of scavenging'' is only qualitative; you made no attempt to quantify such traits.}

\textcolor{blue}{We now emphasise that our scale is qualitative here and throughout the manuscript.}%\textcolor{red}{ in lines (----)}

@@

\item{Introduction: Much of this section seems to follow DeVault's (2003) review paper on scavenging—in fact, there is almost nothing new here that is not covered in that earlier review.}

\textcolor{blue}{We have rewritten the introduction to more accurately reflect the aim of this review i.e. that the scavenging gradient allows us to infer scavenging in the fossil record as well as in modern species. In making this revision we have considerably reduced the inevitable overlap with De Vault (2003).} %TG:

@@

\item{Introduction: You mention that you will use ``other methods in order to discern the most suitable morphologies...''  but you don't say what they are. What other methods are you talking about?}

\textcolor{blue}{We now specify the approaches we have in mind as \textit{``e.g. energetics models, comparative anatomy, palaeontology etc.''} on lines 22-24 with references referring to these methods.}

@@

\item{I think that early on in the paper you need to define obligate and facultative scavengers and then throughout the paper, specify which you are referring to. For example, in the first sentence of the Detection section, you talk about ``known scavengers'', but it is unclear if you really mean obligate scavengers. Nearly all carnivorous vertebrates are scavengers at least to some extent, so you need to elaborate on what you mean when you talk about ``scavengers''.}

\textcolor{blue} {We make the following point in our introduction: \textit{``Indeed, there is no discrete divide between predators and scavengers but rather a continuous gradient. Even vultures, the canonical example of obligate scavengers, can hunt.''} We have also been clearer on this point throughout the paper by removing references to this division. Instead we refer to the gradient of scavenging outlined in the introduction.}

@@

\textcolor{blue}{The hierarchy of our paper wasn't clear as we intended in the first version but thanks to the review process we have now clarified that this is the lead in paragraph to a larger section which has subsections e.g. food processing (see also updated figure 1).}

\end{enumerate}

\section{Reviewer: 2}
This article is a review of the literature what the authors term a ``natural history'' of scavenging.
They have approached the topic from the perspective of ecological variables (and other variables that condition them) in optimal foraging theory including encounter rate and handling time, but also metabolism, locomotion (e.g soaring and swimming), detection, prey availability, competition, and food processing.
They describe many useful examples of the behavior and ecology of obligate and facultative scavengers.
But I think they often go to far in their assumptions in trying to weave these examples together in a synthetic way.
Some examples are inferring scrounging behaviors in flying pterosaurs (pace 11), assuming that hominins used vultures to identify scavenging opportunities (page 11), surmising that scavenging evolved with the earliest tetrapods based on ``potential carrion unexploited by marine vertebrates'' (page 12).
There is a lot of ``these researchers have suggested X'' and then taking that as a given fact.

\bigskip
\textcolor{blue}{One of the central points of our paper is to compare the biology of extant scavengers with extinct species in order to determine if they were suited to scavenging.
And as we discuss in our introduction, because we can't observe the behaviour of extinct species directly we are left to make assumptions about their behaviour. 
Rather than taking them as fact we offer these as possible behaviours that the extinct species engaged in. Our paper proposes these sets of possible scenarios of scavenging to allow for more quantitative tools, such as energetics models, to be used to rule out or support each scenario. This will help us develop a more refined understanding of scavenging in extinct species.
We have also added extra references in support of our claims e.g. \textit {``Thus, given pterosaurs seem to have cohabited in large numbers (Witton 2013), and the theoretical benefits this can have for social foraging in birds (Dermody et al. 2011), it seems probable that scrounging behaviours were seen in the flying pterosaurs as well.''}}

@@

\bigskip

While the authors distinguish between obligate and facultative scavenging, they tend to lump them together when it comes to constructing their arguments.
In the end, is the argument about the former, or the latter? Is the real interest in whether species scavenge at all, what proportion of their resources are obtained by scavenging, or what the conditions are that produce facultative or obligate scavengers?

\bigskip

\textcolor{blue} {This was also raised by reviewer 1 and we thank both reviewers for pointing out this aspect which was unclear in the original manuscript.
We now make the following point in our introduction: \textit{``Indeed, there is no discrete divide between predators and scavengers but rather a continuous gradient. Even vultures, the canonical example of obligate scavengers, can hunt. We have tried to be clearer throughout the paper as well. Indeed, this is a key point of our review paper: to change our view of scavenging from the classic dichotomy of obligate and facultative scavengers, to a sliding scale depending on the species and the ecosystem.''}
We have also been clearer on this point throughout the paper by reducing references to this division between obligate and facultative scavengers where appropriate and again refer to the gradient of scavenging outlined in the introduction}.
%Is this point true. AK Yep! 
\bigskip

@@

They also seem to ignore flexibility in species' behaviors.
For instance, while spotted hyenas are on their highly scavenging side of their Figures 1 and 2, in some ecosystems they hunt significant proportion of their prey.
Similarly, lions can take a large proportion of their prey as scavenged, as the authors note.
But to suggest, as they do in their abstract, that they can apply their scale of scavenging to any species at any time to judge how important scavenging was in its diet is frankly completely ignoring behavioral variability over time and space. 
\bigskip

\textcolor{blue}{It is undoubtedly true that scavengers can be variable in the proportion of carrion they consume but we would argue that species like hyenas have certain characteristics that make this capacity to scavenge  a high proportion of their diet possible.
In contrast, cheetahs do not have a biology that lends itself to scavenging in the wild, due to poor competitive ability etc.
We appreciate that there is a continuum across and among species which we specifically note in this revised version. 
As we note in the above comment, a combination of a species' traits, and the state of the ecosystem they find themselves in will determine their scale of scavenging. 
Search rates can be altered by environmmetal or ecological conditions as well as intrinsic traits of the forager. 
So, far from invalidating our idea, it reinforces it.
Moreover, researchers working in palaeobiology often try to reconstruct the behaviours of extinct species, which themselves are likely to be extremely variable; we are following this approach when we make inferences about ancient systems.}
\bigskip

@@

It is substantially more difficult with fossil species for which we may know far fewer of the variables they list in Figure 1, in a nuanced way.
Figure 2 does not display the diversity of scavengers through time, it displays examples of species that display observed or inferred scavenging behaviors.
Diversity has specific ecological definition(s) that are being ignored here.
\bigskip

\textcolor{blue}{We agree it is more difficult to infer behavior with lower quality data, however by mapping out the variables that are likely to driver high levels of scavenging, the absence of nuanced measures will highlight the extra caution needed when inferring the existence of scavenging in such a circumstance}
\textcolor{blue}{Figure 2 has been removed and figure 1 has been expanded.}

@@

\bigskip

\textcolor{blue}{The issue of the structure of our paper was noted by all reviewers who all had suggestions to improve it. 
We have made a significant effort to delineate all of the main sections and subsections so that our frame of optimal foraging is more apparent.
We have also added the two suggested references to our paper.}

\bigskip
In sum, while I think the aim of the article is a very worthwhile one, I think the authors cannot claim to have produced an all-encompassing model that can predict the presence or level of scavenging in any organism - because I think this simply cannot be done.

\textcolor{blue}{We agree, and do not intend on our framework to act as an all encompassing model of scavenging but instead as a guide to determine a range of possible sceneries with different levels of scavenging. We highlight throughout the manuscript the requirement to use other methods such as energetic models and comparative anatomy in order to make accurate inferences on behaviour.}

@@

%TG: State somewhere here as a response to the reviewer that we don't develop any model in this paper?

Finally, some of the perspectives of this manuscript overlap substantially with parts of Beasley et al. 2015 (pages 108-112), which is cited numerous times in the manuscript.
\bigskip

\textcolor{blue}{The sections of Beasley et al. (2015) are: 1. the evolution of scavengers, 2. competition between scavengers and 3. environmental effects on scavenger ecology.
These are very broad areas so in a review of this sort some overlap is inevitable.
We feel our inclusion of extinct species and systems as well as the novel framing under optimal foraging theory gives this manuscript its novelty. We have paid particular attention towards making the structure of our manuscript more clear and hence differentiating it from Beasley et al. (2015).}
\bigskip

### 2016-08-11 natural history of scavenging.tex
Kev comments included

\textcolor{blue}{Historically, food webs have classified most acts of carnivory as predation events \citep{wilson2011scavenging}. 
This is clearly a mistaken view because of the existence of scavenging, a behaviour displayed by almost all carnivorous vertebrates \citep{devault2003scavenging}. 
Recent research has begun to redress this imbalance by recognising the prevalence of scavenging and its implications for trophic ecology across modern ecosystems \citep{pereira2014facultative,periquet2015lion}.
By increasing multichannel feeding and the number of food web links, scavenging can confer stability to an ecosystem \citep{moleon2015living}. 
Indeed, there is no discrete divide between predators and scavengers but rather a continuous gradient in terms of the proportion of carrion in the diet \citep{pereira2014facultative}.
Even vultures, the canonical example of obligate scavengers, can hunt \citep{margalida2011scavenger}. While it is relatively easy to determine whether a species engages in scavenging through observation, determining the proportion of carrion in the diet requires extensive behavioral data. % (I put this in to placate the reviewer who said it was easy).
Unfortunately, the lack of direct behavioural data makes it even more difficult to discern scavenging from predation among extinct forms where it was surely exhibited by prehistoric vertebrate carnivores.
Some simple heuristics can inform us whether or not the prey was scavenged, for instance, in cases where it was simply too large to have been killed by the ostensible predator \citep{pobiner2008paleoecological}.}
But clearly, a scavenger does not only feed on dead animals too big for it to have hunted.

@@

\begin{figure}[!htbp]
\centering
   \includegraphics[width=1\textwidth]{timeline_figure/timeLine.pdf}
\caption{The diversity of scavengers through time. Each species has either direct evidence for it being a scavenger or would be positioned high up on our scavenging scale. The three lines represent the three different environments (from top to bottom: aerial, terrestrial and aquatic). Time is represented on the horizontal axis with each third representing respectively the Paleozoic (541 - 252 Mya), the Mesozoic (252 - 66 Mya) and the Cenozoic (66 Mya to the present).}
\label{Timeline}
\end{figure}

>>>>

\textcolor{blue}{Historically, food webs have classified most acts of carnivory as predation events \citep{wilson2011scavenging}. 
This is clearly a mistaken view because of the existence of scavenging, a behaviour displayed by almost all carnivorous vertebrates \citep{devault2003scavenging}. 
Recent research has begun to redress this imbalance by recognising the prevalence of scavenging and its implications for trophic ecology across modern ecosystems \citep{pereira2014facultative,periquet2015lion}.
By increasing multichannel feeding and the number of food web links, scavenging can confer stability to an ecosystem \citep{moleon2015living}. 
Indeed, there is no discrete divide between predators and scavengers but rather a continuous gradient in terms of the proportion of carrion in the diet \citep{pereira2014facultative}.
Even vultures, the canonical example of obligate scavengers, can hunt \citep{margalida2011scavenger}. While it is relatively easy to determine whether a species engages in scavenging through observation, determining the proportion of carrion in the diet requires extensive behavioral data. This is because approaches such as stomach content and stable isotope analysis are unable to distinguish between scavenging and predation.} % (I put this in to placate the reviewer who said it was easy).
Unfortunately, the lack of direct behavioural data makes it even more difficult to discern scavenging from predation among extinct forms where it was surely exhibited by prehistoric vertebrate carnivores.
Some simple heuristics can inform us whether or not the prey was scavenged, for instance, in cases where it was simply too large to have been killed by the ostensible predator \citep{pobiner2008paleoecological}.
But clearly, a scavenger does not only feed on dead animals too big for it to have hunted.

@@

%\begin{figure}[!htbp]
%\centering
%   \includegraphics[width=1\textwidth]{timeline_figure/timeLine.pdf}
%\caption{The diversity of scavengers through time. Each species has either direct evidence for it being a scavenger or would be positioned high up on our scavenging scale. The three lines represent the three different environments (from top to bottom: aerial, terrestrial and aquatic). Time is represented on the horizontal axis with each third representing respectively the Paleozoic (541 - 252 Mya), the Mesozoic (252 - 66 Mya) and the Cenozoic (66 Mya to the present).}
%\label{Timeline}
%\end{figure}
